---
title: "1. CD_VOT"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library(tidyverse)

df <- read_tsv("data/speakers.csv")
results <- read_tsv("data/results.tsv")
correspondence <- read_tsv("data/correspondence.tsv")

results %>% 
  left_join(correspondence) %>% 
  left_join(df) %>% 
  filter(!grepl("[tʃrlnm]", folVowel),
       !grepl("[tʃrlnm]", prevVowel)) %>% 
  mutate(repetition = ifelse(repetition == "--undefined--", "", repetition),
         repetition = paste(context, repetition),
         folVowDur = as.double(ifelse(folVowDur == "--undefined--",NA, folVowDur)),
         geminate = ifelse(grepl("[ː:]", stop),"+g", "-g"),
         aff_type = ifelse(grepl("[sz]", stop),"dent", NA),
         aff_type = ifelse(grepl("[ʃʒšžǯ]", stop),"alv", aff_type),
         aff_type = ifelse(grepl("ɬ", stop),"lat", aff_type),
         aff_type = ifelse(grepl("χ", stop),"uv", aff_type),
         affric = ifelse(grepl("ɬ", stop),"affricate", affric),
         affric = ifelse(grepl("χ", stop),"affricate", affric),
         affric = ifelse(poa == "uvular", "plain", affric),
         aff_type = ifelse(grepl("χ", stop),"uv", aff_type),
         poa = ifelse(stop == "ɡ", "velar", poa),
         aff_type = factor(aff_type, levels = c("dent", "alv", "lat", "uv")),
         affric = factor(affric, levels = c("plain", "affricate")),
         voice = ifelse(voice == "voiced", "+v", "-v")) %>% 
  mutate(fric = fric * 1000,
         postfric = postfric*1000,
         folVowDur = folVowDur*1000,
         closdur = closdur*1000,
         VOT = fric + postfric,
         cd_n = closdur/folVowDur,
         vot_n = VOT/folVowDur,
         utterance = paste0(context, "_", repetition),
         poa = factor(poa, levels = c("bilabial", "dental", "velar", "uvular")),
         c_type = ifelse(glott == "glottalic", "ej", voice),
         c_type = ifelse(geminate == "+g", paste0(c_type, ",", "+g"), c_type),
         c_type = factor(c_type, levels = c("+v", "-v", "ej", "-v,+g", "ej,+g"))) ->
  final_df

final_df %>%
  filter(
  repetition != "iso 4",
  repetition != "iso 5",
  repetition != "iso 6",
  repetition != "iso 0",
  repetition != "iso i",
  repetition != "iso NA",
  prevVowel != "b",
  prevVowel != "g",
  prevVowel != "g)",
  prevVowel != "j)",
  prevVowel != "k",
  prevVowel != "(k",
  prevVowel != "k:",
  prevVowel != "k'",
  prevVowel != "(qχ",
  prevVowel != "s",
  prevVowel != "(s",
  prevVowel != "w",
  prevVowel != "z",
  prevVowel != "χ",
  folVowel != "ʔ",
  folVowel != "ɢ",
  folVowel != "ʔ)",
  folVowel != "b",
  folVowel != "j",
  folVowel != "j",
  folVowel != "j)",
  folVowel != "(j)",
  folVowel != "k'",
  folVowel != "p'",
  folVowel != "q",
  folVowel != "qχ",
  folVowel != "w",
  folVowel != "(w",
  folVowel != "w)",
  folVowel != "(w)",
  stop != "(ʔ",
  stop != "(ʔ)",
  stop != "ʔ)",
  stop != "(h",
  stop != "(j",
  stop != "(j)",
  stop != "j)",
  stop != "(s",
  stop != "(w)",
  !is.na(c_type),
  ) ->
  final_df

final_df %>% 
  mutate(stop_label = str_replace_all(final_df$stop, "[ʷˤχ\\(\\)\\?]", "")) ->
  final_df
```

## Absolute values in (medial position)
### CD (medial position)
```{r}
final_df %>% 
  filter(position == "medial") %>%
  ggplot(aes(c_type, closdur, fill = Language, label = stop_label))+
  geom_text(aes(y = 430), alpha = 0.1)+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="bottom")+
  facet_grid(Gender~affric+poa, scale = "free_x")+
  labs(y = "CD (ms)", x = "")
```

### VOT (medial position)
```{r}
final_df %>% 
  filter(position == "medial") %>%
  ggplot(aes(c_type, VOT, fill = Language, label = stop_label))+
  geom_boxplot()+
  geom_text(aes(y = 430), alpha = 0.1)+
  theme_bw()+
  theme(legend.position="bottom")+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  facet_grid(Gender~affric+poa, scale = "free_x")+
  labs(y = "VOT (ms)", x = "")
```

### CD and VOT (medial position)
```{r}
final_df %>% 
  filter(position == "medial") %>%
  ggplot(aes(closdur, VOT, color = Language, label = stop))+
  geom_text()+
  theme_bw()+
  theme(legend.position="bottom")+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  stat_ellipse(aes(group = Language), color = "black")+
  facet_grid(Gender~affric+poa, scale = "free_x")+
  labs(y = "VOT (ms)", x = "CD (ms)")
```

## Relative values in (medial position): СD + VOT
### CD (medial position)
```{r}
final_df %>% 
  filter(position == "medial") %>%
  mutate(rel_cd = closdur/totdur/1000,
         rel_vot = VOT/totdur/1000) %>%
  ggplot(aes(c_type, rel_cd, fill = Language, label = stop))+
  geom_text(aes(y = 1.2), alpha = 0.1)+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="bottom")+
  facet_grid(Gender~affric+poa, scale = "free_x")+
  labs(y = "relative value CD", x = "")
```


### VOT (medial position)
```{r}
final_df %>% 
  filter(position == "medial") %>%
  mutate(rel_cd = closdur/totdur/1000,
         rel_vot = VOT/totdur/1000) %>%
  ggplot(aes(c_type, rel_vot, fill = Language, label = stop))+
  geom_text(aes(y = 1.2), alpha = 0.1)+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="bottom")+
  facet_grid(Gender~affric+poa, scale = "free_x")+
  labs(y = "relative value VOT", x = "")
```

## Relative values in (medial position): by next vowel
### CD (medial position)
```{r}
final_df %>% 
  filter(position == "medial") %>%
  mutate(rel_cd = closdur/folVowDur,
         rel_vot = VOT/folVowDur) %>%
  ggplot(aes(c_type, rel_cd, fill = Language, label = stop))+
  geom_text(aes(y = 5), alpha = 0.1)+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="bottom")+
  facet_grid(Gender~affric+poa, scale = "free_x")+
  labs(y = "relative value CD", x = "")
```


### VOT (medial position)
```{r}
final_df %>% 
  filter(position == "medial") %>%
  mutate(rel_cd = closdur/folVowDur,
         rel_vot = VOT/folVowDur) %>%
  ggplot(aes(c_type, rel_vot, fill = Language, label = stop))+
  geom_text(aes(y = 5), alpha = 0.1)+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="bottom")+
  facet_grid(Gender~affric+poa, scale = "free_x")+
  labs(y = "relative value VOT", x = "")
```

## Relative values in (medial position): by whole stimulus

I don't have such information... I need Sven added it to the script. And idially both to the i and to the j version.