---
title: 'Daghestanian stops: VOT, CD'
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_position: right
    code_folding: hide
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message=FALSE,
                      warning= FALSE,
                      fig.width=10.4,
                      fig.height=7)
```

# Get data

```{r}
library(tidyverse)

df <- read_tsv("speakers.csv")

results <- read_tsv("results.tsv")
correspondence <- read_tsv("correspondence.tsv")

results %>% 
  left_join(correspondence) %>% 
  left_join(df) %>% 
  filter(!grepl("[tʃrlnm]", folVowel),
       !grepl("[tʃrlnm]", prevVowel)) %>% 
  mutate(repetition = ifelse(repetition == "--undefined--", "", repetition),
         repetition = paste(context, repetition),
         folVowDur = as.double(ifelse(folVowDur == "--undefined--",NA, folVowDur)),
         geminate = ifelse(grepl("[ː:]", stop),"+g", "-g"),
         aff_type = ifelse(grepl("[sz]", stop),"dent", NA),
         aff_type = ifelse(grepl("[ʃʒšžǯ]", stop),"alv", aff_type),
         aff_type = ifelse(grepl("ɬ", stop),"lat", aff_type),
         aff_type = ifelse(grepl("χ", stop),"uv", aff_type),
         affric = ifelse(grepl("ɬ", stop),"affricate", affric),
         affric = ifelse(grepl("χ", stop),"affricate", affric),
         affric = ifelse(poa == "uvular", "plain", affric),
         aff_type = ifelse(grepl("χ", stop),"uv", aff_type),
         aff_type = factor(aff_type, levels = c("dent", "alv", "lat", "uv")),
         affric = factor(affric, levels = c("plain", "affricate")),
         voice = ifelse(voice == "voiced", "+v", "-v")) %>% 
  mutate(fric = fric * 1000,
         postfric = postfric*1000,
         folVowDur = folVowDur*1000,
         closdur = closdur*1000,
         VOT = fric + postfric,
         cd_n = closdur/folVowDur,
         vot_n = VOT/folVowDur,
         utterance = paste0(context, "_", repetition),
         poa = factor(poa, levels = c("bilabial", "dental", "velar", "uvular")),
         c_type = ifelse(glott == "glottalic", "ej", voice),
         c_type = ifelse(geminate == "+g", paste0(c_type, ",", "+g"), c_type),
         c_type = factor(c_type, levels = c("+v", "-v", "ej", "-v,+g", "ej,+g"))) ->
  final_df

final_df %>% 
  filter(repetition != "iso 4",
         repetition != "iso 5",
         repetition != "iso 6",
         repetition != "iso 0",
         repetition != "iso i",
         repetition != "iso NA") ->
  final_df

```

# Absolute values
## Absolute values of CD (medial)

During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated.

### Andi

```{r}
speaker <- unique(final_df[, 31:32])
speaker <- speaker[complete.cases(speaker),]

final_df %>% 
  filter(id == unlist(speaker[1, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey",
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[1, 1],
                       speaker[1, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[2, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[2, 1],
                       speaker[2, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[3, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[3, 1],
                                              speaker[3, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[4, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[4, 1],
                       speaker[4, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[5, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[5, 1],
                       speaker[5, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[6, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[6, 1],
                       speaker[6, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[7, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[7, 1],
                       speaker[7, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[8, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[8, 1],
                       speaker[8, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[9, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[9, 1],
                       speaker[9, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Rutul

```{r}
final_df %>% 
  filter(id == unlist(speaker[10, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[10, 1],
                       speaker[10, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[11, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[11, 1],
                       speaker[11, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[12, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[12, 1],
                       speaker[12, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[13, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[13, 1],
                       speaker[13, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[14, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[14, 1],
                       speaker[14, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[15, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[15, 1],
                       speaker[15, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[16, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[16, 1],
                       speaker[16, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[17, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[17, 1],
                       speaker[17, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[18, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[18, 1],
                       speaker[18, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[19, 1]), position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, closdur))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker[19, 1],
                       speaker[19, 2],
                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Aggregated
```{r}
final_df %>% 
  filter(position == "medial") %>%
  ggplot(aes(c_type, closdur, color = Language))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on all speakers"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```


## Absolute values of VOT (medial)
During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated. I added a new lines with 30 and 160 ms from (L&C 2001)

### Andi

```{r}
final_df %>% 
  filter(id == unlist(speaker[1, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[1, 1],
                                              speaker[1, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[2, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[2, 1],
                                              speaker[2, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[3, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[3, 1],
                                              speaker[3, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[4, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[4, 1],
                                              speaker[4, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[5, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[5, 1],
                                              speaker[5, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[6, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[6, 1],
                                              speaker[6, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[7, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[7, 1],
                                              speaker[7, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[8, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[8, 1],
                                              speaker[8, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[9, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[9, 1],
                                              speaker[9, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Rutul

```{r}
final_df %>% 
  filter(id == unlist(speaker[10, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[10, 1],
                                              speaker[10, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[11, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[11, 1],
                                              speaker[11, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[12, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[12, 1],
                                              speaker[12, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[13, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[13, 1],
                                              speaker[13, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[14, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[14, 1],
                                              speaker[14, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[15, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[15, 1],
                                              speaker[15, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[16, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[16, 1],
                                              speaker[16, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[17, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[17, 1],
                                              speaker[17, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[18, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[18, 1],
                                              speaker[18, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[19, 1]), position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa, label = stop))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker[19, 1],
                                              speaker[19, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Aggregated
```{r}
final_df %>% 
  filter(position == "medial") %>%
  ggplot(aes(c_type, VOT, color = Language))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on all speakers"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```


## Absolute values of CD ~ VOT (medial)

During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated.

### Andi

```{r}
final_df %>% 
  filter(id == unlist(speaker[1, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                                      speaker[1, 1],
                                                      speaker[1, 2],
                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[2, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                                      speaker[2, 1],
                                                      speaker[2, 2],
                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[3, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                                      speaker[3, 1],
                                                      speaker[3, 2],
                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[4, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[4, 1],
                                                       speaker[4, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[5, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[5, 1],
                                                       speaker[5, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[6, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[6, 1],
                                                       speaker[6, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[7, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                                      speaker[7, 1],
                                                      speaker[7, 2],
                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[8, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[8, 1],
                                                       speaker[8, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[9, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[9, 1],
                                                       speaker[9, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Rutul

```{r}
final_df %>% 
  filter(id == unlist(speaker[10, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[10, 1],
                                                       speaker[10, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[11, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[11, 1],
                                                       speaker[11, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[12, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[12, 1],
                                                       speaker[12, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[13, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[13, 1],
                                                       speaker[13, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[14, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[14, 1],
                                                       speaker[14, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[15, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[15, 1],
                                                       speaker[15, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[16, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[16, 1],
                                                       speaker[16, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[17, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[17, 1],
                                                       speaker[17, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[18, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[18, 1],
                                                       speaker[18, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[19, 1]), position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type, label = stop))+
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(closdur, VOT))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)",  caption = paste("medial position, based on",
                                                       speaker[19, 1],
                                                       speaker[19, 2],
                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```


# Relative values
## Relative values of CD (medial)

During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated.


### Andi

```{r}
final_df %>% 
  filter(id == unlist(speaker[1, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[1, 1],
                                              speaker[1, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[2, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[2, 1],
                                              speaker[2, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[3, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[3, 1],
                                              speaker[3, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[4, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[4, 1],
                                              speaker[4, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[5, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[5, 1],
                                              speaker[5, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[6, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[6, 1],
                                              speaker[6, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[7, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[7, 1],
                                              speaker[7, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[8, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[8, 1],
                                              speaker[8, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[9, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[9, 1],
                                              speaker[9, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Rutul

```{r}
final_df %>% 
  filter(id == unlist(speaker[10, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[10, 1],
                                              speaker[10, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[11, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[11, 1],
                                              speaker[11, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[12, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[12, 1],
                                              speaker[12, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[13, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[13, 1],
                                              speaker[13, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[14, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[14, 1],
                                              speaker[14, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[15, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[15, 1],
                                              speaker[15, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[16, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[16, 1],
                                              speaker[16, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[17, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[17, 1],
                                              speaker[17, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[18, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[18, 1],
                                              speaker[18, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[19, 1]), position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, cd_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[19, 1],
                                              speaker[19, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Aggregated
```{r}
final_df %>% 
  filter(position == "medial") %>%
  ggplot(aes(c_type, cd_n, color = Language))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on all speakers"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

## Relative values of VOT (medial)
During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated. I added a new lines with 30 and 160 ms from (L&C 2001)

### Andi

```{r}
final_df %>% 
  filter(id == unlist(speaker[1, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[1, 1],
                                              speaker[1, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[2, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[2, 1],
                                              speaker[2, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[3, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[3, 1],
                                              speaker[3, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[4, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[4, 1],
                                              speaker[4, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[5, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[5, 1],
                                              speaker[5, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[6, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[6, 1],
                                              speaker[6, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[7, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[7, 1],
                                              speaker[7, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[8, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[8, 1],
                                              speaker[8, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[9, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[9, 1],
                                              speaker[9, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Rutul

```{r}
final_df %>% 
  filter(id == unlist(speaker[10, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[10, 1],
                                              speaker[10, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[11, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                              speaker[11, 1],
                                              speaker[11, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[12, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[12, 1],
                                              speaker[12, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[13, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[13, 1],
                                              speaker[13, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[14, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[14, 1],
                                              speaker[14, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[15, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[15, 1],
                                              speaker[15, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[16, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[16, 1],
                                              speaker[16, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[17, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[17, 1],
                                              speaker[17, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[18, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[18, 1],
                                              speaker[18, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[19, 1]), position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa, label = stop))+
  geom_boxplot(data = final_df[, -31], color = "grey", alpha = 0.2,
            aes(c_type, vot_n))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "",  caption = paste("medial position, based on",
                                              speaker[19, 1],
                                              speaker[19, 2],
                                              "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```


### Aggregated
```{r}
final_df %>% 
  filter(position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = Language))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on all speakers"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```


## Relative values of CD ~ VOT (medial)

During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated.

### Andi

```{r}
final_df %>% 
  filter(id == unlist(speaker[1, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
                                                                      speaker[1, 1],
                                                                      speaker[1, 2],
                                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[2, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
                                                                      speaker[2, 1],
                                                                      speaker[2, 2],
                                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[3, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
                                                                      speaker[3, 1],
                                                                      speaker[3, 2],
                                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[4, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
                                                                      speaker[4, 1],
                                                                      speaker[4, 2],
                                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[5, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[5, 1],
                                                                       speaker[5, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[6, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[6, 1],
                                                                       speaker[6, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[7, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
                                                                      speaker[7, 1],
                                                                      speaker[7, 2],
                                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[8, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[8, 1],
                                                                       speaker[8, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[9, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[9, 1],
                                                                       speaker[9, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

### Rutul

```{r}
final_df %>% 
  filter(id == unlist(speaker[10, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[10, 1],
                                                                       speaker[10, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[11, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
                                                                      speaker[11, 1],
                                                                      speaker[11, 2],
                                                                      "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[12, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[12, 1],
                                                                       speaker[12, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[13, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[13, 1],
                                                                       speaker[13, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[14, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[14, 1],
                                                                       speaker[14, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[15, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[15, 1],
                                                                       speaker[15, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>% 
  filter(id == unlist(speaker[16, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "CD (normalized)",  caption = paste("medial position, based on",
                                                                       speaker[16, 1],
                                                                       speaker[16, 2],
                                                                       "speaker"), scale = "free_y")+
  facet_grid(repetition~affric+poa)
```

```{r}
final_df %>%
  filter(id == unlist(speaker[17, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw() +
  theme(legend.position = "top") +
  labs(
    y = "VOT (normalized)",
    x = "CD (normalized)",
    caption = paste("medial position, based on",
                    speaker[17, 1],
                    speaker[17, 2],
                    "speaker"), scale = "free_y"
  ) +
  facet_grid(repetition ~ affric + poa)
```

```{r}
final_df %>%
  filter(id == unlist(speaker[18, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw() +
  theme(legend.position = "top") +
  labs(
    y = "VOT (normalized)",
    x = "CD (normalized)",
    caption = paste("medial position, based on",
                    speaker[18, 1],
                    speaker[18, 2],
                    "speaker"), scale = "free_y"
  ) +
  facet_grid(repetition ~ affric + poa)
```

```{r}
final_df %>%
  filter(id == unlist(speaker[19, 1]), position == "medial") %>%
  ggplot(aes(cd_n, vot_n, color = c_type, label = stop)) +
  geom_text(data = final_df[, -31], color = "grey", alpha = 0.2,
               aes(cd_n, vot_n, label = stop))+
  geom_text(show.legend = F)+
  theme_bw() +
  theme(legend.position = "top") +
  labs(
    y = "VOT (normalized)",
    x = "CD (normalized)",
    caption = paste("medial position, based on",
                    speaker[19, 1],
                    speaker[19, 2],
                    "speaker"), scale = "free_y") +
  facet_grid(repetition ~ affric + poa)
```

## Phonological position comparison

There are a lot of 0 values in non-medial position. I filter them out.

```{r}
final_df %>% 
  filter(closdur > 0,
         position != "final") %>% 
  ggplot(aes(c_type, closdur, color = Language))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on all speakers"))+
  facet_grid(position~affric+poa, scale = "free")
```

```{r}
final_df %>% 
  filter(VOT > 0,
         position != "final") %>% 
  ggplot(aes(c_type, VOT, color = Language))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on all speakers"), scale = "free_y")+
  facet_grid(position~affric+poa)
```


```{r}
final_df %>%
  filter(cd_n > 0,
         position != "final") %>% 
  ggplot(aes(c_type, cd_n, color = Language))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (normalized)", x = "", caption = paste("medial position, based on all speakers"), scale = "free_y")+
  facet_grid(position~affric+poa)
```

```{r}
final_df %>% 
  filter(vot_n > 0,
         position != "final") %>%   
  ggplot(aes(c_type, vot_n, color = Language))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on all speakers"), scale = "free_y")+
  facet_grid(position~affric+poa)
```