---
title: 'Daghestanian stops: VOT, CD'
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_position: right
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message=FALSE,
                      warning= FALSE,
                      fig.width=10.4,
                      fig.height=7)
```

# Get data

```{r}
library(tidyverse)
df <- read_tsv("speakers.csv")

results <- read_tsv("results.tsv")
correspondence <- read_tsv("correspondence.tsv")

results %>% 
  left_join(correspondence) %>% 
  left_join(df) %>% 
  filter(!grepl("[tʃrlnm]", folVowel),
       !grepl("[tʃrlnm]", prevVowel)) %>% 
  mutate(repetition = ifelse(repetition == "--undefined--", "", repetition),
         repetition = paste(context, repetition),
         folVowDur = as.double(ifelse(folVowDur == "--undefined--",NA, folVowDur)),
         geminate = ifelse(grepl("[ː:]", stop),"+g", "-g"),
         aff_type = ifelse(grepl("[sz]", stop),"dent", NA),
         aff_type = ifelse(grepl("[ʃʒšžǯ]", stop),"alv", aff_type),
         aff_type = ifelse(grepl("ɬ", stop),"lat", aff_type),
         aff_type = ifelse(grepl("χ", stop),"uv", aff_type),
         affric = ifelse(grepl("ɬ", stop),"affricate", affric),
         affric = ifelse(grepl("χ", stop),"affricate", affric),
         aff_type = ifelse(grepl("χ", stop),"uv", aff_type),
         aff_type = factor(aff_type, levels = c("dent", "alv", "lat", "uv")),
         affric = factor(affric, levels = c("plain", "affricate")),
         voice = ifelse(voice == "voiced", "+v", "-v")) %>% 
  mutate(fric = fric * 1000,
         postfric = postfric*1000,
         folVowDur = folVowDur*1000,
         closdur = closdur*1000,
         VOT = fric + postfric,
         cd_n = closdur/folVowDur,
         vot_n = VOT/folVowDur,
         utterance = paste0(context, "_", repetition),
         poa = factor(poa, levels = c("bilabial", "dental", "velar", "uvular")),
         c_type = ifelse(glott == "glottalic", "ej", voice),
         c_type = ifelse(geminate == "+g", paste0(c_type, ",", "+g"), c_type),
         c_type = factor(c_type, levels = c("+v", "-v", "ej", "-v,+g", "ej,+g"))) ->
  final_df
```

# Absolute values
## Absolute values of CD (medial)

During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated.

```{r}
speaker <- "m_19"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_14"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_11"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_22"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_24"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_16"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_8"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_75"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_84"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_81"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_91"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_92"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_94"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, closdur, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "CD (ms)", x = "", caption = paste("medial position, based on",
                       speaker,
                       "Rutul speaker"))+
  facet_grid(repetition~affric+poa)

```

## Absolute values of VOT (medial)
During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated. I added a new lines with 30 and 160 ms from (L&C 2001)

```{r}
speaker <- "m_19"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_14"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_11"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_22"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_24"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_16"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_8"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_75"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_84"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_81"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_91"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+   
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_92"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_94"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, VOT, color = poa))+
  geom_hline(yintercept = 30, lty = 2)+
  geom_hline(yintercept = 160, lty = 2)+ 
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)

```

## Absolute values of CD ~ VOT (medial)

During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated.

```{r}
speaker <- "m_19"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_14"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_11"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_22"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_24"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_16"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_8"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_75"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_84"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_81"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_91"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_92"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_94"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(closdur, VOT, color = c_type))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (ms)", x = "CD (ms)", caption = paste("medial position, based on",
                                              speaker,
                              "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

# Relative values
## Relative values of CD (medial)

During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated.


```{r}
speaker <- "m_19"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_14"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_11"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_22"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_24"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_16"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_8"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_75"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_84"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_81"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_91"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_92"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_94"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)

```



## Relative values of VOT (medial)
During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated. I added a new lines with 30 and 160 ms from (L&C 2001)


```{r}
speaker <- "m_19"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_14"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_11"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_22"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_24"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_16"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_8"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Andi speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_75"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_84"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_81"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_91"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_92"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_94"
final_df %>% 
  filter(id == speaker, position == "medial") %>%
  ggplot(aes(c_type, vot_n, color = poa))+
  geom_point()+
  theme_bw()+
  theme(legend.position="top")+
  labs(y = "VOT (normalized)", x = "", caption = paste("medial position, based on",
                                                      speaker,
                                                      "Rutul speaker"))+
  facet_grid(repetition~affric+poa)

```




## Relative values of CD ~ VOT (medial)

During the presentation I've filtered out the 0 values, but here I leave them. All of them should be investigated.

```{r}
speaker <- "m_19"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Andi speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_14"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Andi speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_11"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Andi speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_22"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Andi speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_24"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Andi speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_16"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Andi speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "f_8"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Andi speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_75"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Rutul speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_84"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Rutul speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_81"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Rutul speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_91"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Rutul speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_92"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Rutul speaker"))+
facet_grid(repetition~affric+poa)
```

```{r}
speaker <- "m_94"
final_df %>% 
filter(id == speaker, position == "medial") %>%
ggplot(aes(cd_n, vot_n, color = c_type))+
geom_point()+
theme_bw()+
theme(legend.position="top")+
labs(y = "VOT (normalized)", x = "CD (normalized)", caption = paste("medial position, based on",
speaker,
"Rutul speaker"))+
facet_grid(repetition~affric+poa)
```
